A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-22 paper/paper.tex
paper: minor nits

\section{Semi-simplicial sets, semi-cubical sets and a generalization}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}. We will proceed to explain the mathematical objects we have formalized. % TODO: well-known: can we find a reference?

@@

More generally, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension. In the latter, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on. In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by 0 while the components of the lifted copy are postfixed by $\kstar$.

>>>>

\section{Semi-simplicial and semi-cubical sets}
It is well-known that simplicial sets exist purely in the imagination of the mathematician, as every simplicial set has an infinite number of degenerate simplices. What we have formalized is \emph{augmented semi-simplicial} sets~\cite{fri08}, and \emph{semi-cubical} sets~\cite{grandis03,buchholtz17}. We will proceed to explain the mathematical objects we have formalized. % TODO: well-known: can we find a reference?

@@

More generally, the standard augmented $(n+1)$-semi-simplex can be obtained by taking a copy of the standard augmented $n$-semi-simplex serving as the base and glueing on top of it another copy of it lifted by one dimension. In the latter, the color becomes an extra point, the points become lines connecting the points of the base to the extra point and so on. In particular, the components of the base are those of the standard augmented $n$-semi-simplex postfixed by $0$ while the components of the lifted copy are postfixed by $\kstar$.
